Capstone Movielens Report

### 2025-12-15 reports/capstone-movielens.site/02-0.methods.Rmd
Functions described: `regularize.train_UMGYD_effect`, `regularize.train_UMGYD_effect.cv`.

As a result of executing these functions, we will obtain the following datasets (detailed in [Appendix B: Models Training Datasets]), which we will use throughout *This Project*:

@@

::: {.noteblock data-latex=""}
The $K$ value for the *K-Fold Cross-Validation* we use in *This Project* is determined by the length of the list composing the [`edx_CV` Object]. In our case, the length of the `edx_CV` is 5, meaning we use *5-Fold Cross-Validation*.
:::

>>>>

As a result of executing these functions, we will obtain the following datasets (detailed in [Appendix B: Models Training Datasets]), which we will use throughout *this Project*:

@@

::: {.noteblock data-latex=""}
The $K$ value for the *K-Fold Cross-Validation* we use in *this Project* is determined by the length of the list composing the [`edx_CV` Object]. In our case, the length of the `edx_CV` is 5, meaning we use *5-Fold Cross-Validation*.
:::

### 2025-12-15 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd
Functions described: `regularize.train_UMGYD_effect`, `regularize.train_UMGYD_effect.cv`.

::: {.noteblock data-latex=""}
In the code snippets above, we use the [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) and [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) functions described in the [UMGYE Model: Utility Functions] section of [Appendix A](#appndx_a) to *This Report*.
:::

>>>>

::: {.noteblock data-latex=""}
In the code snippets above, we use the [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) and [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) functions described in the [UMGYE Model: Utility Functions] section of [Appendix A](#appndx_a) to *this Report*.
:::
